mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-21 Draft3.Rmd
parentheses around inf + (-inf)

```{r, results='asis'}
term <- quote(1 + 2L + "a" + a + abc + phi + Phi + varphi + hat(b)[i, j]^2L
              + NaN + NA + TRUE + FALSE + Inf + -Inf)
mathout(term)
```

>>>>

```{r, results='asis'}
term <- quote(1 + 2L + "a" + a + abc + phi + Phi + varphi + hat(b)[i, j]^2L)
mathout(term)

term <- quote(NaN + NA + TRUE + FALSE + Inf + -Inf)
mathout(term)
```
